---
title: "01-exercises"
author: "Christopher Brown"
date: "April 6, 2016"
output: html_document
---


## Exercise 1:

Write a function (f) that takes a vector of numbers, **x**, and returns a vector of numbers such that each element containing the product of every element of x except the element of x with the same index. 


### Example 

    > x <- c( 1, 5, 2, 8 ) 
    > f(x) 
    [1] 80 16 40 10
    # 5*2*8, 1*2*8, 1*5*8, 1*2*5  


### Solution 

```{r}
f <- function(x) {
  
  # ...
  len=length(x)#Length of input vector
z=vector(mode="numeric",length=len)
for (i in 1:len){
      y=1
      q=1
      for(k in 1:len){
        q=x[k]
        if(i==k){q=1}
        y=y*q
      }
  z[i]=y
}
return(z)
}

```
    


## Exercise 2

Write a function f(x) to accept an integer vector, and returns a vector with those numbers except for: 
   multiples of 3 replaced by "Fizz" 
   multiples of 5 replaced by "Buzz" 
   multiples of 3 and 5 replaced by "FizzBuzz""
   
### Example

    > x <- 1:20
    > f(1:20) 
    # 1 2 Fizz 4 Buzz Fizz 7 8 Fizz Buzz 11 Fizz 13 14 FizzBuzz 16 17 Fizz 19 Buzz


### Solution

```{r}
f <- function(x) {
  # ...
  len=x 
d=vector(,len)
for (i in 1:len){
  
  if(i %% 3 ==0 & i %% 5==0){
    d[i]="FIZZBUZZ"
  }
  else if(i %% 3 ==0){
    d[i]="FIZZ"
  }
  
  else if(i %% 5 ==0){
    d[i]="BUZZ"
  }
    else{d[i]=i}

}
return(d)
}
```
