---
title: "NYCFlights: Arrival Delay Logictic Model"
author: "[Your Name]"
date: "[Today's Date]"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Loading the necessary libraries
```{r,echo=FALSE}
library(caTools)
library("dplyr")
library("data.table")
library("ggplot2")



```
## Logsitic and Inverse Logistic Transformation 

- Write an R function for the logistic function. The function should accept a `numeric` vector with values `[-Inf,Inf]` and produce a numeric vector in the the range `[0,1]`.

```{r}
sample_fun=function(x){
  y=1/(1+exp(-x))
  return(y)
}

sample_fun(c(-10:10))
```


- Plot the logistic function from  `[-10,10]`
```{r}
plot(sample_fun(c(-10:10)),c(-10:10))

```

- Write a R function for the inverse logistic function. The function should accept a `numeric` vector with values `[0,1]` and prodcuce a numeric vector in the range `[-Inf,Inf]`

```{r}
inv_log=function(x){
  y=log(x/(1-x))
  return(y)
}

inv_log(c(0:1))
```

- Plot the Inverse Logistic function from `[0,1]`
```{r}
g=seq(.02,.8,.001)

plot(inv_log(g),g)
```
**Hint:** For plotting curves see `?graphics::curve` or `?ggplot2::stat_function`

```{r "Logistic and Inverse Logistic" }

```


# NYCFlights Model

Using the rectangular data that you created from the earlier assignment and following theexample from the text and class, create a model for arr_delay >= 22 minutes. Describe/Explain each of the steps and show all work.

# Step 1
```{r,echo=FALSE}

flights_dt=fread("C:\\Users\\Vani\\Downloads\\UCB\\CSX460\\02-building-blocks\\02-exercise-nycflights\\data\\flights.csv")

#reading the AIRPORT dataset

airports_dt=fread("C:\\Users\\Vani\\Downloads\\UCB\\CSX460\\02-building-blocks\\02-exercise-nycflights\\data\\airports.csv")

#Reading the PLANES data set

planes_dt=fread("C:\\Users\\Vani\\Downloads\\UCB\\CSX460\\02-building-blocks\\02-exercise-nycflights\\data\\planes.csv")
planes_dt

#reading the WEATHER dataset
weather_dt=fread("C:\\Users\\Vani\\Downloads\\UCB\\CSX460\\02-building-blocks\\02-exercise-nycflights\\data\\weather.csv")

#Joining to make a single data table

Aviation=left_join(flights_dt,weather_dt,by=c("origin","year","month","day","hour") ) %>%
  left_join(planes_dt, by='tailnum') %>% 
  left_join(airports_dt, by=c('origin'='faa') ) %>% 
  left_join(airports_dt, by=c('dest'='faa') ) 

```





KNIT YOUR DOCUMENT AS *HTML* AND SUBMIT IT AND THE `Rmd` file to your repository.   
```{r}

Aviation_new=mutate(Aviation,arr_delay_22=ifelse(arr_delay>22,0,1))

```
#Step 2

#Data preparation

#Selecting the required variables
```{r}
Aviation1=Aviation_new[, c("arr_delay","arr_delay_22", "visib","precip","humid","temp","dep_delay","arr_time","carrier","origin","dest","air_time","sched_arr_time","month","distance")]

```
#Plotting the graph to understnad the skewness

```{r}
qplot(Aviation1$arr_delay)
```

#Find the corelation matrics
```{r}
numeric_column=Aviation1 %>% sapply(is.numeric) %>%  which() %>% names()
Aviation1[,numeric_column,] %>% cor(use="pairwise.complete.obs")

```

Sheduled_arr_time and dep_delay is highly correlated.
Sheduled_arr_time and arr_time is highly corelated




#Step 3
Splitting the data in to testing and training set
```{r}
set.seed(1000)

split=sample.split(Aviation1$arr_delay_22,SplitRatio = .65)
train=subset(Aviation1,split==TRUE)
test=subset(Aviation1,split==FALSE)
  
```


# Step 4

Applying the log4istic function

```{r}
Aviation1_Log=glm(arr_delay_22 ~ dep_delay+carrier+air_time+visib+precip+temp+humid ,data=train,family = binomial)

summary(Aviation1_Log)

```
#Step 5

Prdictions on test set

```{r}
predicttest=predict(Aviation1_Log,type="response",newdata = test)

#Creating confusion Matrics to measure accuracy
table(test$arr_delay_22,predicttest>.5)



```

#Step 6 Accuracy of prediction
```{r}

#Accuracy

(15527+90055)/(15527+6529+2019+90055)
```
Accuracy


#Step 7
Comparing with the Navie model

```{r}
#Most frequent outcome here is that there wont be delay which is greater than 22 min
#Accuracy of the baseline model
(15527+6529)/(15527+6529+2019+90055)

```

# Question:

Is this a good model?

Yes,Because the accuracy of the model created is 93%,but the accuracy of the navie model is just 19 %.

# PART B:

Your model should be good at explaining tardiness. Now, assume that your job is to predict arrival delays a month in advance. You can no longer use all the features in your model. Retrain your model using only features that will be *known* only a month in advance of the departure time.  Show all steps as above.

Following attributes will be available a month in advance:

carrier+air_time+visib+precip+temp+humid

#Step 1

Creating a new model based on the known attributes

```{r}
Aviation1_LogB=glm(arr_delay_22 ~ carrier+air_time+visib+precip+temp+humid ,data=train,family = binomial)

summary(Aviation1_LogB)

```
#Step 2

Prdictions on test set

```{r}
predicttestB=predict(Aviation1_LogB,type="response",newdata = test)

#Creating confusion Matrics to measure accuracy
table(test$arr_delay_22,predicttestB>.5)



```

#Step 3 Accuracy of prediction
```{r}

#Accuracy

(375+91602)/(375+21681+472+91602)
```
Accuracy


#Step 4
Comparing with the Navie model

```{r}
#Most frequent outcome here is that there wont be delay which is greater than 22 min
#Accuracy of the baseline model
(375+21681)/(375+21681+472+91602)

```

# Question:

Is this a good model?

Yes,Because the accuracy of the model created is 91%,but the accuracy of the navie model is just 19 %.

