---
title: "mproving Model Perfromance / Tuning Parameters"
author: "Vani P jyothy"
date: "5/13/2017"
output: pdf_document
---

```{r init, warning=FALSE, echo=FALSE, message=FALSE}
library(rpart)
library(caret)
library("ROCR")
library(data.table)
library(magrittr)
library(dplyr)
library(rpart)
library(rpart.plot)
library(kknn)
library(C50)
# .. Additional libraries
```

## Tuning Parameter

Generically and regardless of model type, what are the purposes of a model tuning parameters?

Tuning paameter decides how a particular model is fit.It can effect the bias-variance trade-off.BIAS measures how close the model comes to the true value.High bias ???means  poor fit. VARIANCE is the stability of the model, susceptibility to new values.High variance means ???poor fit

## Caret Models

This assignment demonstrates the use of caret for constructing models. 
Each model should be built and compared using using `Kappa` as the performance
metric calculated using 10-fold repeated cross-validation with 3 folds.

Using the rectangular data that you created for the NYCFlights to create a model
for arr_delay >= 15 minutes.


```{r,echo=FALSE}

flights_dt=fread("C:\\Users\\Vani\\Downloads\\UCB\\CSX460\\02-building-blocks\\02-exercise-nycflights\\data\\flights.csv")

#reading the AIRPORT dataset

airports_dt=fread("C:\\Users\\Vani\\Downloads\\UCB\\CSX460\\02-building-blocks\\02-exercise-nycflights\\data\\airports.csv")

#Reading the PLANES data set

planes_dt=fread("C:\\Users\\Vani\\Downloads\\UCB\\CSX460\\02-building-blocks\\02-exercise-nycflights\\data\\planes.csv")
planes_dt

#reading the WEATHER dataset
weather_dt=fread("C:\\Users\\Vani\\Downloads\\UCB\\CSX460\\02-building-blocks\\02-exercise-nycflights\\data\\weather.csv")

#Joining to make a single data table

Aviation=left_join(flights_dt,weather_dt,by=c("origin","year","month","day","hour") ) %>%
  left_join(planes_dt, by='tailnum') %>% 
  left_join(airports_dt, by=c('origin'='faa') ) %>% 
  left_join(airports_dt, by=c('dest'='faa') )

Aviation_new=mutate(Aviation,arr_delay_15=ifelse(arr_delay>15,0,1))
Aviation1=Aviation_new[, c("arr_delay","arr_delay_15", "visib","precip","humid","temp","dep_delay","arr_time","carrier","origin","dest","air_time","sched_arr_time","month","distance")]


Aviation1=subset(Aviation1, (!is.na(Aviation1[,2])))

```
#Data set used after doing the necessary preprocessing and only selecting the required fiels

```{r}

str(Aviation1)

summary(Aviation1)

```
# Splitting the data into tesing and training data set
```{r}
set.seed(1)
Train <- createDataPartition(Aviation1$arr_delay_15, p=0.1, list=FALSE,times=1)
training <- Aviation1[ Train, ]
testing <- Aviation1[ -Train, ]

#Converting the output variable to a factor variable
training$arr_delay_15=factor(training$arr_delay_15)
testing$arr_delay_15=factor(testing$arr_delay_15)

x=na.omit(training)

y=sample_n(x,3000)
```
## Caret Models

This assignment demonstrates the use of caret for constructing models. Each model should be built and compared using using `Kappa` as the performance
metric calculated using 10-fold repeated cross-validation with 3 folds.

Using the rectangular data that you created for the NYCFlights to create a model
for arr_delay >= 15 minutes.

- glm

```{r}
train_control<- trainControl(method="cv", number=3, savePredictions = TRUE)

fit_glm=train(arr_delay_15 ~ dep_delay+carrier+air_time+visib+precip+temp+humid,data=training,trControl=train_control, method="glm", family="binomial",na.action=na.pass)

fit_glm
```


- rpart

```{r}
train_control_rpart<- trainControl(method="cv", number=3, savePredictions = TRUE)


fit_rpart=train(arr_delay_15 ~ dep_delay+carrier+air_time+visib+precip+temp+humid,data=training,trControl=train_control_rpart, method="rpart",na.action=na.pass)




fit_rpart
```
knn

```{r}
train_control_knn<- trainControl(method="cv", number=3, savePredictions = TRUE)


fit_knn=train(arr_delay_15 ~ dep_delay+carrier+air_time+visib+precip+temp+humid,data=y, method="knn",na.action=na.pass)


fit_knn
```
Random forest

```{r}
fit_rf=train(arr_delay_15 ~ dep_delay+carrier+air_time+visib+precip+temp+humid,data=y,method="rf",
                trControl=trainControl(method="cv",number=3),
                prox=TRUE,allowParallel=TRUE)

fit_rf
```


C50

```{r}
fit_c50=train(arr_delay_15 ~ dep_delay+carrier+air_time+visib+precip+temp+humid,data=y,method="C5.0",
                trControl=trainControl(method="cv",number=3))

fit_c50
```

Which model is the best?

Tree model is the best because of its interpretebility.