---
title: "Classification Mettrics"
author: "Vani P Jyothy"
date: "October 5, 2015"
output:
  html_document: default
  pdf_document: default
---


**KNIT YOUR DOCUMENT AS *HTML* AND SUBMIT IT AND THE `Rmd` file.** 
 

#Loading the necessary libraries
```{r,echo=FALSE}
library(caTools)
library("dplyr")
library("data.table")
library("ggplot2")



```
## Classification Metrics Functions 

Write functions of `y` and `y_hat` to calculate the following classification metrics

* True Positive Rate  
* False Positive Rate
* True Negative Rate  
* False Negative Rate 
* Sensitivity 
* Specificity 
* Recall 
* Precision
* Prevalence 
* Accuracy
* Kappa


1)True Positive Rate

```{r}
test_fun=function(y,y_hat,matric)
{
if(matric=="TPRA"){
z=table(y,y_hat>.5)  
x=z[1,1]/(z[1,1]+z[1,2])
return(x)
}
  
  if(matric=="FPRA"){
z=table(y,y_hat>.5)  
x=z[2,1]/(z[2,1]+z[2,2])
return(x)
  }
  
  if(matric=="TNRA"){
z=table(y,y_hat>.5)  
x=z[2,2]/(z[2,1]+z[2,2])
return(x)
  }
  
  if(matric=="FNRA"){
z=table(y,y_hat>.5)  
x=z[1,2]/(z[1,1]+z[1,2])
return(x)
  }
  
  if(matric=="sensitivity"){
z=table(y,y_hat>.5)  
x=z[1,1]/(z[1,1]+z[1,2])
return(x)
  }
  
  if(matric=="specificity"){
z=table(y,y_hat>.5)  
x=z[2,2]/(z[2,1]+z[2,2])
return(x)
  }
  
  if(matric=="recall"){
z=table(y,y_hat>.5)  
x=z[1,1]/(z[1,1]+z[1,2])
return(x)
  }
  
  if(matric=="precision"){
z=table(y,y_hat>.5)  
x=z[1,1]/(z[1,1]+z[2,1])
return(x)
  }
  
  if(matric=="prevalance"){
z=table(y,y_hat>.5)  
x=(z[1,1]+z[1,2])/(z[1,1]+z[1,2]+z[2,1]+z[2,2])
return(x)
  }
  
  if(matric=="accuracy"){
z=table(y,y_hat>.5)  
x=(z[1,1]+z[2,2])/(z[1,1]+z[1,2]+z[2,1]+z[2,2])
return(x)}
}

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.



# Step 1
```{r,echo=FALSE}

flights_dt=fread("C:\\Users\\Vani\\Downloads\\UCB\\CSX460\\02-building-blocks\\02-exercise-nycflights\\data\\flights.csv")

#reading the AIRPORT dataset

airports_dt=fread("C:\\Users\\Vani\\Downloads\\UCB\\CSX460\\02-building-blocks\\02-exercise-nycflights\\data\\airports.csv")

#Reading the PLANES data set

planes_dt=fread("C:\\Users\\Vani\\Downloads\\UCB\\CSX460\\02-building-blocks\\02-exercise-nycflights\\data\\planes.csv")
planes_dt

#reading the WEATHER dataset
weather_dt=fread("C:\\Users\\Vani\\Downloads\\UCB\\CSX460\\02-building-blocks\\02-exercise-nycflights\\data\\weather.csv")

#Joining to make a single data table

Aviation=left_join(flights_dt,weather_dt,by=c("origin","year","month","day","hour") ) %>%
  left_join(planes_dt, by='tailnum') %>% 
  left_join(airports_dt, by=c('origin'='faa') ) %>% 
  left_join(airports_dt, by=c('dest'='faa') ) 


Aviation_new=mutate(Aviation,arr_delay_22=ifelse(arr_delay>22,0,1))

#Step 2

#Data preparation

#Selecting the required variables

Aviation1=Aviation_new[, c("arr_delay","arr_delay_22", "visib","precip","humid","temp","dep_delay","arr_time","carrier","origin","dest","air_time","sched_arr_time","month","distance")]


#Splitting the data in to testing and training set
set.seed(1000)

split=sample.split(Aviation1$arr_delay_22,SplitRatio = .65)
train=subset(Aviation1,split==TRUE)
test=subset(Aviation1,split==FALSE)



# Step 4

#Applying the log4istic function

Aviation1_Log=glm(arr_delay_22 ~ dep_delay+carrier+air_time+visib+precip+temp+humid ,data=train,family = binomial)


#Step 5

#Prdictions on test set

predicttest=predict(Aviation1_Log,type="response",newdata = test)
```
## Usage 

```{r}
test_fun(test$arr_delay_22,predicttest,"sensitivity")

```



#True Positive Rate
```{r}

test_fun(test$arr_delay_22,predicttest,"TPRA")

```
#False Positive Rate

```{r}
test_fun(test$arr_delay_22,predicttest,"FPRA")

```
# True Negative Rate  

```{r}
test_fun(test$arr_delay_22,predicttest,"TNRA")

```
* False Negative Rate 

```{r}

test_fun(test$arr_delay_22,predicttest,"FNRA")

```
* Sensitivity 
```{r}

test_fun(test$arr_delay_22,predicttest,"sensitivity")
```

* Specificity 

```{r}
test_fun(test$arr_delay_22,predicttest,"specificity")

```
* Recall 

```{r}
test_fun(test$arr_delay_22,predicttest,"recall")

```
* Precision
```{r}
test_fun(test$arr_delay_22,predicttest,"precision")

```
* Prevalence 

```{r}
test_fun(test$arr_delay_22,predicttest,"prevalance")

```
* Accuracy

```{r}
test_fun(test$arr_delay_22,predicttest,"accuracy")

```
* Kappa
