---
title: "Caret / Recursive Partitioning"
author: "Vani P jyothy"
date: "5/13/2017"
output: pdf_document
---

```{r init, warning=FALSE, echo=FALSE, message=FALSE}
library(rpart)
library(caret)
library("ROCR")
library(data.table)
library(magrittr)
library(dplyr)
library(rpart)
library(rpart.plot)
# .. Additional libraries
```


## Exercise 1: caret/logistic regression (5 points)

Rebuild your logistic regression model from the previous week, this time using the `caret` package. 
```{r,echo=FALSE}

flights_dt=fread("C:\\Users\\Vani\\Downloads\\UCB\\CSX460\\02-building-blocks\\02-exercise-nycflights\\data\\flights.csv")

#reading the AIRPORT dataset

airports_dt=fread("C:\\Users\\Vani\\Downloads\\UCB\\CSX460\\02-building-blocks\\02-exercise-nycflights\\data\\airports.csv")

#Reading the PLANES data set

planes_dt=fread("C:\\Users\\Vani\\Downloads\\UCB\\CSX460\\02-building-blocks\\02-exercise-nycflights\\data\\planes.csv")
planes_dt

#reading the WEATHER dataset
weather_dt=fread("C:\\Users\\Vani\\Downloads\\UCB\\CSX460\\02-building-blocks\\02-exercise-nycflights\\data\\weather.csv")

#Joining to make a single data table

Aviation=left_join(flights_dt,weather_dt,by=c("origin","year","month","day","hour") ) %>%
  left_join(planes_dt, by='tailnum') %>% 
  left_join(airports_dt, by=c('origin'='faa') ) %>% 
  left_join(airports_dt, by=c('dest'='faa') )

Aviation_new=mutate(Aviation,arr_delay_22=ifelse(arr_delay>22,0,1))
Aviation1=Aviation_new[, c("arr_delay","arr_delay_22", "visib","precip","humid","temp","dep_delay","arr_time","carrier","origin","dest","air_time","sched_arr_time","month","distance")]


Aviation1=subset(Aviation1, (!is.na(Aviation1[,2])))

```
#Data set used after doing the necessary preprocessing and only selecting the required fiels

```{r}

str(Aviation1)

```
# Splitting the data into tesing and training data set
```{r}
set.seed(1)
Train <- createDataPartition(Aviation1$arr_delay_22, p=0.6, list=FALSE,times=1)
training <- Aviation1[ Train, ]
testing <- Aviation1[ -Train, ]

#Converting the output variable to a factor variable
training$arr_delay_22=factor(training$arr_delay_22)
testing$arr_delay_22=factor(testing$arr_delay_22)

```

#Building the logistic regression model using the Caret package
```{r}

fit=train(arr_delay_22 ~ dep_delay+carrier+air_time+visib+precip+temp+humid,data=training, method="glm", family="binomial",na.action=na.pass)


```
- Calculate the training or apparent performance of the model. 

```{r}
#Removing the NA values in the testing data
testing1=na.omit(testing)
predicttest=predict(fit,newdata = testing1)
confusionMatrix(predicttest,testing1$arr_delay_22)

```
- Create a ROC Curve for your model

```{r}

#predicttest1=predict(fit,newdata = testing1,type="response")
rocpred=prediction(as.numeric(predicttest),testing1$arr_delay_22)
rocperf=performance(rocpred,"tpr","fpr")
plot(rocperf,colorize=TRUE,print.cutoffs.at=seq(0,1,.1),text.adj=c(-0.2,1.7))


```


## Exercise 2: caret/rpart (5 points)

Using the `caret` and `rpart` packages, create a **classification** model for flight delays using your NYC FLight data. Your solution should include:

##Using  rpart to train a model.
```{r}
flight_tree=rpart(arr_delay_22 ~ air_time+visib+precip+temp+humid+dep_delay+carrier,data=training,method = "class",minbucket=10)

```
##Using caret to train the model

```{r}

fit_tree_caret=train(arr_delay_22 ~ dep_delay+carrier+air_time+visib+precip+temp+humid,data=training, method="rpart",na.action=na.pass)

```

- An articulation of the the problem your are 

The problem here is to make a decision tree to predict the arrival delay of the flights data.Model is trained,so that it will predict whether a particular flight will have delay >22 min 

- An naive model

Our Naive model is the most frequent outcome.That is there wont be any delay greater than 22 min


- An unbiased calculation of the performance metric


#Testing the model using the testing data set using rpart function

```{r}
predictflight=predict(flight_tree,newdata = testing1,type="class")

# Calculating the accuracy of the model

table(testing1$arr_delay_22,predictflight)

#Accuracy of the prediction

(17833+102783)/(17833+102783+7294+2554)

#Accuracy of the Naive model(most frequent outcome,which is that there is no delay >22 min)
(2554+102783)/(17833+102783+7294+2554)


```

- A plot of your model -- (the actual tree; there are several ways to do this)
```{r}

prp(flight_tree)

```
- A discussion of your model 

The accuracy of the NAive model is 80%,where as the accuracy of the model that was trained by decision tree is 92%.Since it beats the accuracy of the Naive model,the model build is fairly good.

#Testing the model using the testing data set using Caet function

```{r}
predictflight_caret_tree=predict(fit_tree_caret,newdata = testing1)

# Calculating the accuracy of the model

table(testing1$arr_delay_22,predictflight_caret_tree)

#Accuracy of the prediction

(16948+103680)/(16948+103680+8179+1657)

#Accuracy of the Naive model(most frequent outcome,which is that there is no delay >22 min)
(1657+103680)/(16948+103680+8179+1657)


```
### Questions:

- Discuss the difference between the models and why you would use one model over the other?

The accuracy is almost same using caret or rpart

- How might you produce an ROC type curve for the *rpart* model? 
```{r}
predictROC=predict(flight_tree,newdata = testing1)

head(predictROC)



```

```{r}

predRoctree=prediction(predictROC[,2],testing1$arr_delay_22)

perftree=performance(predRoctree,"tpr","fpr")

plot(perftree)


```