---
title: "Resampling"
author: "Vani P jyothy"
date: "October 5, 2015"
output: html_document
---

**KNIT YOUR DOCUMENT AS *HTML* AND SUBMIT IT AND THE `Rmd` file**

## Resampling

`x` is a random variable. We want to not only know what the `mean(x)` is but want to calculate the uncertainty of `mean(x)`.  Measuring the uncertainty requires repeated measurements of `mean(x)`.

- Calculate the mean of `x`.
- Calculte the `sd( mean(x) )` using the **using 10-fold resampling**.  Create your own folds, show your work.
- Calculte the `sd( mean(x) )` using the **using 10 bootstrap sample**.  Create your own folds, show your work. 

##10 fold bootstrap
```{r}
set.seed(1) 

x <- runif(20,1,20)

mn <- vector(mode="numeric", length=10)
std <- vector(mode="numeric", length=10)
for(i in 1:10)
{
y=sample(x,10,replace=TRUE)
mn[i]=mean(y)
std[i]=sd(y)
}

```
#SD of individual samples
```{r}
std
```
#Mean of individual samples
```{r}
mn
```
#Mean of the original vectior X after sampling
```{r}
mean(mn)

```
#SD of the original vector X after sampling
```{r}
mean(std)

```
#Mean with out samapling
```{r}
mean(x)

```
#SD without resampling

```{r}
sd(x)

```

##10 fold cross sampling

```{r}
set.seed(1) 

x <- runif(20,1,20)
mnc <- vector(mode="numeric", length=10)
c <- vector(mode="numeric", length=10)
for(j in 1:10)
{
z=sample(x,10,replace=FALSE)
mnc[j]=mean(z);
c[j]=sd(z)
}

```
#SD of individual sample
```{r}
c

```
#Mean of individual sample
```{r}
mnc
```
#Mean of the original vectior X after sampling
```{r}
mean(mnc)

```
#SD of the original vector X after sampling
```{r}
mean(c)

```
#Mean with out resmapling
```{r}
mean(x)

```
#SD without resampling

```{r}
sd(x)

```


### Your answers here: 

- sd_cv   is: 5.516
- sd_boot is: 5.205
